\documentclass[12pt]{article}

\usepackage{amsmath, amssymb, amsthm, enumerate, graphicx}
\usepackage[usenames,dvipsnames]{color}
\usepackage{bm}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{float}
\usepackage{graphics}
\setlength{\marginparwidth}{2.15cm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{setspace}
\usepackage{parskip}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, automata}
\usepackage{pgfplots}
\usepackage[font=scriptsize]{subcaption}
\usepackage{float}
\usepackage[]{algorithm2e}
\usepackage{environ}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{titling}
\usepackage{url}
\usepackage{xcolor}
\usepackage{lipsum}
\usepackage{lastpage}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{comment}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{marvosym}
\usepackage{wrapfig}
\usepackage{datetime}
\usepackage[many]{tcolorbox}
\usepackage{array}
\usepackage{multirow}
\usepackage{wasysym}
\usepackage{cancel}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{color}
\usepackage[thinlines]{easytable}
\usepackage{lastpage}

\newcommand{\R}{\mathbb{R}}
\newcommand{\blackcircle}{\tikz\draw[black,fill=black] (0,0) circle (1ex);}
\renewcommand{\circle}{\tikz\draw[black] (0,0) circle (1ex);}

\usetikzlibrary{positioning,calc}

\newtcolorbox[]{solution}[1][]{%
    breakable,
    enhanced,
    colback=white,
    %title=Solution,
    #1
}

\begin{document}
\section*{}
\begin{center}
  \centerline{\textsc{\LARGE  Homework 6 Template}}
\end{center}

Use this template to record your answers for Homework 6.  Add your answers using \LaTeX and then save your document as a PDF to upload to Gradescope.  You are required to use this template to submit your answers.  \textbf{You should not alter this template in any way} other than to insert your solutions.  You must submit all \pageref{LastPage} pages of this template to Gradescope.  Do not remove the instructions page(s).  Altering this template or including your solutions outside of the provided boxes can result in your assignment being graded incorrectly.  You may lose points if you do not follow these instructions.

You should also save your code as a .py or .zip file and upload it to the \textbf{separate} Gradescope coding assignment. Remember to mark all teammates on \textbf{both} assignment uploads through Gradescope.

\section*{Instructions for Specific Problem Types}

On this homework, you must fill in (a) blank(s) for each problem; please make sure your final answer is fully included in the given space.  \textbf{Do not change the size of the box provided.}  For short answer questions you should \textbf{not} include your work in your solution.  Only provide an explanation or proof if specifically asked.  Otherwise, your assignment may not be graded correctly, and points may be deducted from your assignment.

\section*{Problem 0: Collaborators}
Enter your team's names and Andrew IDs in the boxes below.  If you do not do this, you may lose points on your assignment.

Name 1: \begin{tcolorbox}[fit,height=1cm, width=5cm, blank, borderline={1pt}{1pt},nobeforeafter]
    \begin{center}
    \vspace{3mm}
    \large{}
    \end{center}
\end{tcolorbox}
Andrew ID 1: \begin{tcolorbox}[fit,height=1cm, width=5cm, blank, borderline={1pt}{1pt},nobeforeafter]
    \begin{center}
    \vspace{3mm}
    \large{}
    \end{center}
\end{tcolorbox}
    \\
Name 2: \begin{tcolorbox}[fit,height=1cm, width=5cm, blank, borderline={1pt}{1pt},nobeforeafter]
    \begin{center}
    \vspace{3mm}
    \large{}
    \end{center}
\end{tcolorbox}
Andrew ID 2: \begin{tcolorbox}[fit,height=1cm, width=5cm, blank, borderline={1pt}{1pt},nobeforeafter]
    \begin{center}
    \vspace{3mm}
    \large{}
    \end{center}
\end{tcolorbox} \\
Name 3: \begin{tcolorbox}[fit,height=1cm, width=5cm, blank, borderline={1pt}{1pt},nobeforeafter]
    \begin{center}
    \vspace{3mm}
    \large{}
    \end{center}
\end{tcolorbox}
Andrew ID 3: \begin{tcolorbox}[fit,height=1cm, width=5cm, blank, borderline={1pt}{1pt},nobeforeafter]
    \begin{center}
    \vspace{3mm}
    \large{}
    \end{center}
\end{tcolorbox} \\
\vspace{0.5cm}
\vspace{0.5cm}

\newpage
\section*{Problem 1: Crowd-Sourcing Quiz Questions}
Please submit your four questions and answers to each using the following form (once per question):\\
{\centerline{\url{https://forms.gle/xKqhqaxNaXHYRS2c7}}}

\section*{Problem 2: Types of Uncertainty}

\subsection*{2.1 Combined Variance}
\begin{solution}[height=8cm]
% YOUR SOLUTION
\end{solution}

\subsection*{2.2.1 Uncertainty in a Dynamics Model}
\begin{solution}[height=5cm]
% YOUR SOLUTION
\end{solution}

\subsection*{2.2.2 Estimating the Terms}
\begin{solution}[height=6cm]
% YOUR SOLUTION
\end{solution}

\subsection*{2.2.3 Connection with Model-Based RL}
\begin{solution}[height=6cm]
% YOUR SOLUTION
\end{solution}

\subsection*{2.2.4 Connection with Exploration Bonuses}
\begin{solution}[height=5cm]
% YOUR SOLUTION
\end{solution}

\clearpage
\section*{Problem 3: Bayesian Neural Networks}

\subsection*{3.1 Uncertainty in BNNs}
\begin{solution}[height=7cm]
% YOUR SOLUTION
\end{solution}

\subsection*{3.2 An Objective for BNNs}
\begin{solution}[height=5cm]
% YOUR SOLUTION
\end{solution}

\clearpage
\subsection*{3.3 REINFORCE for BNNs}
\begin{solution}[height=9cm]
% YOUR SOLUTION
\end{solution}

\subsection*{3.4 Variational Inference for BNNs}
\begin{solution}[height=9cm]
% YOUR SOLUTION
\end{solution}



\clearpage
\section*{Problem 4: LQR and iLQR}

\subsection*{4.1 LQR}
\begin{solution}[height=8cm]
% YOUR SOLUTION
\end{solution}

\subsection*{4.2 iLQR}
\begin{solution}[height=8cm]
% YOUR SOLUTION
\end{solution}

\subsection*{4.3 Comparing LQR and iLQR}
\begin{solution}[height=5cm]
% YOUR SOLUTION
\end{solution}

\end{document}